Leadership across cultures and contexts: an exploratory analysis

### 2020-05-12 leadership_across_cultures_contexts.Rmd
A bit of rearranging in conclusion.

Leadership and social influence are expected to be associated with particular suites of individual qualities and functions, which potentially covary by cultural or social context, personality, or other inter-individual variation [@cheng_two_2013; @von_rueden_roots_2014; @hogan_personality_2020; @lukaszewski_extraversion_2015; @henrich_evolution_2001; @bass_handbook_1990].

Our systematic cross-cultural results support many aspects of influential evolutionary theories of leadership, but offer new direction for the expansion and synthesis of leadership theories.

@@

The feature of leader organizational functions aligns with the many evolutionary theories of leadership that emphasize the role of leaders in organizing collective actions [e.g., @hooper_theory_2010; @van_vugt_cognitive_2007; @glowacki_formation_2016; for review, see @garfield_evolutionary_2019]. In the ethnographic record such functions includes controlling and facilitating economic productivity and ensuring collective actions do not overly conflict with individual or household-level goals, such as among the Tukano of the Brazilian Amazon, where @sq19-018 [p. 127] notes:

@@

### Some notes

[NEED TO INTEGRATE]
These results provide a framework for further work on evolutionarily relevant costs and benefits of leadership, and suggests leaders-follower dynamics should continue to be prioritized in evolutionary models of demography, group dynamics, social complexity and inequality, cooperation and punishment, and resource exchange [c.f., @bird_variability_2019; @ember_our_2018; @micheletti_modelling_2020; @smith_cultural_2020; @birch2017philosophy; @marlowe_more_2008; @henrich_markets_2010; @mace_co-evolution_1998; @mace_phylogenetic_2005; @mattison_evolution_2016]

@@

>>>>

Leadership and social influence are expected to be associated with particular suites of individual qualities and functions, which potentially covary by cultural or social context, personality, or other inter-individual variation [@cheng_two_2013; @von_rueden_roots_2014; @hogan_personality_2020; @lukaszewski_extraversion_2015; @henrich_evolution_2001; @bass_handbook_1990]. Our systematic cross-cultural results support many aspects of influential evolutionary theories of leadership, but offer new direction for the expansion and synthesis of leadership theories.

@@

The feature of leader organizational functions also aligns with the many evolutionary theories of leadership that emphasize the role of leaders in organizing collective actions [e.g., @hooper_theory_2010; @van_vugt_cognitive_2007; @glowacki_formation_2016; for review, see @garfield_evolutionary_2019]. In the ethnographic record such functions includes controlling and facilitating economic productivity and ensuring collective actions do not overly conflict with individual or household-level goals, such as among the Tukano of the Brazilian Amazon, where @sq19-018 [p. 127] notes:

@@

@@

<!-- IS THIS NEEDED? HERE ??? -->
These results provide a framework for further work on evolutionarily relevant costs and benefits of leadership, and suggests leaders-follower dynamics should continue to be prioritized in evolutionary models of demography, group dynamics, social complexity and inequality, cooperation and punishment, and resource exchange [c.f., @bird_variability_2019; @ember_our_2018; @micheletti_modelling_2020; @smith_cultural_2020; @birch2017philosophy; @marlowe_more_2008; @henrich_markets_2010; @mace_co-evolution_1998; @mace_phylogenetic_2005; @mattison_evolution_2016]
